Deep Learning and Bayesian Modeling

### 2021-05-23 DeepLearningAndBayesianSoftware.Rmd
hopefully final

I intend this to be an evolving document with periodic updates at it's github repo at [https://github.com/breckbaldwin/bayesianImpactMetrics](https://github.com/breckbaldwin/bayesianImpactMetrics) where it lives as `DeepLearningAndBayesianSoftware.Rmd`, is rendered as `DeepLearningAndBayesianSoftware.html` and is viewable as [https://breckbaldwin.github.io/bayesianImpactMetrics/DeepLearningAndBayesianSoftware.html](https://breckbaldwin.github.io/bayesianImpactMetrics/DeepLearningAndBayesianSoftware.html). All source code is viewable in the .Rmd document.

>>>>

I intend this to be an evolving document with periodic updates at it's github repo at [https://github.com/breckbaldwin/ScientificSoftwareImpactMetrics](https://github.com/breckbaldwin/ScientificSoftwareImpactMetrics) where it lives as `DeepLearningAndBayesianSoftware.Rmd`, is rendered as `DeepLearningAndBayesianSoftware.html` and is viewable as [https://breckbaldwin.github.io/ScientificSoftwareImpactMetrics/DeepLearningAndBayesianSoftware.html](https://breckbaldwin.github.io/ScientificSoftwareImpactMetrics/DeepLearningAndBayesianSoftware.html). Note that github pages changes urls around in odd ways for the rendered view of hte html page. All source code is viewable in the .Rmd document.
